\documentclass[11pt,english]{article}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Packages
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% Package imports are stored in /assets/base-packages.tex
% Packages specific to this pset can be imported here.

\listfiles
\input{assets/base-packages.tex}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Shortcuts
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{assets/mysymbols}
\input{assets/math_definition.tex}
\renewcommand{\hide}[1]{}
\usepackage{graphicx}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Title / Author
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}
\title{CS 4644/7643: Deep Learning\\
Spring 2022 \\
Problem Set 1}

% NOTE: Any changes to instructor, TAs, or piazza link should be done in the file below
\input{assets/instructor-and-TAs}
\date{Due: Monday, January 31, 11:59pm}
\maketitle

\paragraph*{Instructions}
\begin{enumerate}
\item We will be using Gradescope to collect your assignments.  Please read the following instructions for submitting to Gradescope carefully!
     \begin{itemize}
          % \item
               % This assignment has 10 total problems/sub-problems. Questions 1-7 are theory questions, while 8-10 are programming
               % questions. 
          \item
               For the \textbf{HW1 Writeup} component on Gradescope, you could upload one single PDF containing the answers to all the theory questions and the report for coding problems. \textbf{However, the solution to each problem/subproblem must be on a separate page. When submitting to Gradescope, please make sure to mark the page(s) corresponding to each problem/sub-problem.} Likewise, the pages of the report must also be marked to their corresponding subproblems.
          \item
               For the \textbf{HW1 Code} component on Gradescope, 
               please use the \texttt{collect\_submission.sh} script provided and upload the resulting \textbf{hw1\_code.zip} on Gradescope. Please make sure you have saved the most recent version of your codes.
          \item
               Note: This is a large class and Gradescope's assignment segmentation features are essential.
               Failure to follow these instructions may result in parts of your assignment not being graded.
               We will not entertain regrading requests for failure to follow instructions.

               % Please read \url{https://stats200.stanford.edu/gradescope_tips.pdf} for additional information on submitting to Gradescope.
     \end{itemize}

\item
     \LaTeX'd solutions are strongly encouraged (solution template
     available in the zip file in HW1 under the Assignments tab on Canvas), but scanned handwritten copies are acceptable. Hard copies are \textbf{not} accepted.


\item We generally encourage you to collaborate with other students.

You may talk to a friend,
discuss the questions and potential directions for solving them. However, you need to write
your own solutions and code separately, and \emph{not} as a group activity.
Please list the students you collaborated with. \\ \\

\end{enumerate}
\newpage

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Body
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Collaborators [0.5 points]}

\input{question-bank/Misc/collaborators}


\section{Optimization}

\begin{enumerate}[start]

\item
\textbf{[2 points]}
\input{question-bank/Optimization/levelsets}

\item
\textbf{[2 points]}
\input{question-bank/Optimization/local_min_gradient}

\item
\textbf{[3 points]}
\input{question-bank/Optimization/global_min_convex}

\item
\textbf{[2 points]}
\input{question-bank/Optimization/softmax_gradient}

\item
\textbf{[3 points: Extra credit for both 4644 and 7643]}
\input{question-bank/Optimization/softmax_simplex_projection}

\end{enumerate}

\section{Directed Acyclic Graphs (DAG)}
\input{question-bank/Misc/DAG_background}

\begin{enumerate}[resume]

\item
\textbf{[3 points]}
\input{question-bank/Misc/DAG_topological1}

\item
\textbf{[3 points]}
\input{question-bank/Misc/DAG_topological2}

\end{enumerate}

\section{Paper Review [Extra credit for 4644, regular credit for 7643]}

%%%% Point values defined in the file below %%%%
\input{question-bank/Paper_Reviews/NeurIPS_2019_weighted_agnostic}

\section{Implement and train a network on MNIST}

\begin{enumerate}[resume]

\item
\textbf{[20 points]}
\input{question-bank/Coding/learn_MNIST}

\end{enumerate}

\end{document}
